Native advertising as a content marketing strategy

### 2024-09-10 analysis/paper/paper.Rmd
weiter

>>>>

```{r analysis, echo=F, eval=FALSE, message=F , warning= FALSE, results='hide'}

# make a nice historam of the reach in ggplot

# Create the histogram

ggplot(dta, aes(x = REACH)) + 
  geom_histogram(binwidth = 1500, fill = "blue", color = "black") +
  labs(title = "Reach of Portals", x = "Reach", y = "Frequency") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
    panel.grid.major.x = element_blank(),  # Remove vertical grid lines
    panel.border = element_rect(fill = NA, color = "black")  # Add border
  )

# filter this data to max reach of 30000

ggplot(filtered_dta, aes(x = REACH)) +
  geom_histogram(binwidth = 1500, fill = "blue", color = "black") +
  labs(title = "Reach of Portals", x = "Reach", y = "Frequency") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
    panel.grid.major.x = element_blank(),  # Remove vertical grid lines
    panel.border = element_rect(fill = NA, color = "black")  # Add border
  )

shapiro.test(filtered_dta$REACH)

library(car)

leveneTest(mean_reach ~ text, data = result)

anova_model <- aov(REACH ~ CLICKBAIT, data = dta)
summary(anova_model)

TukeyHSD(anova_model)

kruskal.test(REACH ~ CLICKBAIT, data = dta)
